---
title: "Acala AUSD Trace"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    social: menu
    source_code: embed
---

```{css custom1, echo=FALSE}
.dataTables_scrollBody {
    max-height: 100% !important;
}
```

```{r global, include=FALSE}


library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)

library(dygraphs)
library(kableExtra)
library(formattable)
library(lubridate)
library(flexdashboard)
library(DT)
library(subscanr)
library(formattable)
library(ghql)
x <- GraphqlClient$new()

# Helper function to concat
`%+%` <- function(a, b) paste0(a, b)

library(reticulate)
# use_python("/opt/homebrew/bin/python3.9")

```

```{python, include=FALSE}

import pandas as pd
from datetime import date
import requests
import json
from substrateinterface.utils.ss58 import ss58_decode, ss58_encode
from scalecodec.base import ScaleBytes #, ScaleDecoder, RuntimeConfigurationObject, ScaleType
from substrateinterface import SubstrateInterface, Keypair, ExtrinsicReceipt
pd.set_option('display.max_columns', None)


def getLoans(network, start_block_number, end_block_number):
  if network.lower() == 'acala':
    url = 'wss://acala-rpc-3.aca-api.network/ws'
  else: 
    url = 'wss://karura.polkawallet.io'      
  substrate = SubstrateInterface(url)
  data = []
  for b in range(int(start_block_number), int(end_block_number)):
    events = substrate.query('System', 'Events', block_hash=substrate.get_block_hash(b))
    e = events.decode()
    for i in range(len(e)):
      if e[i]['module_id'] == 'Loans' and e[i]['event_id'] == 'PositionUpdated':
        # print(f'***** {i}')
        # print(e[i])
        outi = {"address": e[i]['attributes'][0], "CurrencyId": e[i]['attributes'][1], 'collateral_adjustment': e[i]['attributes'][2], 'debit_adjustment': e[i]['attributes'][3]}
        data.append(outi)  
  out = pd.DataFrame(data)
  return(out)

# getLoans(network = "Acala", start_block_number = 1638215, end_block_number = 1639493)

      
  # for event in events:
  #   if event.value['module_id'] == 'Loans' and event.value['event_id'] == 'PositionUpdated':
  #     extrinsic_receipt = substrate.retrieve_extrinsic_by_identifier(f"{block_number}-{event.value['extrinsic_idx']}")
  #     tmp = extrinsic_receipt.extrinsic.decode()
  #     tmp2 = tmp['call']['call_args']
  #     tmp2[0]['value']['currency_id']
  #     
  #   tmp = json.loads(events.decode()[1])
  #     
  #     out = {"address": tmp['address'], "CurrencyId": tmp2[1]['value'], 'collateral_adjustment': tmp2[1]['value'], 'debit_adjustment': tmp2[2]['value']}
  # return out

def getExtrinsic(network):
  if network.lower() == 'acala':
    url = 'wss://acala-rpc-0.aca-api.network'
  else: 
    url = 'wss://karura.polkawallet.io'      
  substrate = SubstrateInterface(url)
  data = []
  for j in range(len(r.events)):
    receipt = substrate.retrieve_extrinsic_by_identifier(r.events[j])
    for i in range(len(receipt.triggered_events)):
      tmp = receipt.triggered_events[i].decode()
      if tmp['event_id'] == "PositionUpdated":
        outi = {"AccountId": tmp['attributes'][0], "CurrencyId": tmp['attributes'][1], 'DepositAmount': tmp['attributes'][2], 'DebitAmount': tmp['attributes'][3]}
        data.append(outi)
        
  out = pd.DataFrame(data)
  return(out)

# getExtrinsic("Acala", ["1507944-2","1507944-2","1507944-2"])

# Convert ss58 address from one chain to another 
# (i.e. Substrate=42, Polkadot=0, Kusama=2, Acala=10, Karura=8)
def ss58_convert(addr, fromChain, toChain):
  pk = ss58_decode(addr, valid_ss58_format = int(fromChain))
  output = ss58_encode(pk, ss58_format = int(toChain))
  return output

# Convert ss58 address from one chain to another 
# (i.e. Substrate=42, Polkadot=0, Kusama=2, Acala=10, Karura=8)
def pk_convert(pk, toChain):
  output = ss58_encode(pk, ss58_format = int(toChain))
  return output


# encoded_call_hash = "0x6d02840058f7c213df83660d39112b03073a01b69a4d7836bbba6b12b7f5797c9996645701f873abd040b35516e469d08ef973c27a19b8c199b706c1514917e681655a1d33ac83c6b716acb890f0e1517be1899089effe7636e13dbaa22083e08a71102b88140000000e04008203020874000b007083d05d0666000083408df266ef340000000000000000000000000000000000000000000000000000"
# substrate = SubstrateInterface('wss://karura.polkawallet.io')
# extrinsic_data = ScaleBytes(encoded_call_hash)
# extrinsic = substrate.create_scale_object("Extrinsic", extrinsic_data)
# print(extrinsic.decode())

def getSubscanAPI(API_ENDPOINT, API_KEY, module, call, row, page):
  # API_ENDPOINT = "https://karura.api.subscan.io/api/v2/scan/extrinsics"
  # API_KEY = "3c62fde82f543d3560ec33223c47c95d"
  # module = "transactionPayment"
  # call = "with_fee_currency"
  header = {"X-API-Key": API_KEY}
  data = {"row": int(row), "page": int(page), "module": module, "call": call}
  r = requests.post(url = API_ENDPOINT, headers = header, data = data)
  if r.json()['message'] == 'Success':
    return r.json()['data']['extrinsics']

# def getSubscanExtrinsic(API_ENDPOINT, API_KEY, extrinsic_hash):
#   API_ENDPOINT = "https://karura.api.subscan.io/api/v2/scan/extrinsic"
#   API_KEY = "3c62fde82f543d3560ec33223c47c95d"
#   extrinsic_hash = "0x18180de22e733b9a92236c64310c61fa5ef7324d5440835fd9bfe6b0c174b51b"
#   index = "2399379-2"
#   header = {"X-API-Key": API_KEY}
#   # data = {"hash": extrinsic_hash}
#   data = {"extrinsic_index": index}
#   r = requests.post(url = API_ENDPOINT, headers = header, data = data)
#   if r.json()['message'] == 'Success':
#     return r.json()['data']['extrinsics']

def getTotalIssuance(network):
    if network.lower() == 'acala':
        url = 'wss://acala-rpc-0.aca-api.network'
        token = 'LDOT'
        decimals = 10
    else: 
        url = 'wss://karura.polkawallet.io'      
        token = 'LKSM'
        decimals = 12
    
    data = []
    substrate = SubstrateInterface(url)
    for j in block_history:
        hash = substrate.get_block_hash(block_id = int(j))
        # timestamp = substrate.query(module='Timestamp',storage_function='Now',block_hash=hash).value
        # Issuance
        liquid = substrate.query(module='Tokens',storage_function='TotalIssuance', params = [{'Token': token}], block_hash = hash).value / 10**decimals
        
        try:
            homa = substrate.query_map(module='Homa',storage_function='StakingLedgers', block_hash = hash)
            amount = 0
            for res in homa:
                amount += res[1].value['bonded']
        except:
            amount = 0
        outi = {"network": network, "Block": j, 'liquid_amount': liquid, 'staking_amount': amount / 10**decimals}
        data.append(outi)
    out = pd.DataFrame(data)
    return out

```



```{r honzon, cache = TRUE, include=FALSE}

# tmp <- py$getLoans(network = "Acala", start_block_number = "1638215", end_block_number = "1639493")



# r_sq <- getRewards_acala("Acala", window = 4)
trace <- fromJSON("~/subquery/trace1/scripts/src/trace/claim-rewards-events.json", flatten = TRUE)
trace <- as.data.table(trace) %>%
  setnames(names(trace), names(trace) %+% "_sq")

getRewards_acala_incentives <- function(network, window, filter = '', endpage = 2000, staging = FALSE) {

  # network="acala"; window = 1; filter = ''; endpage = 2

  if (tolower(network) == 'acala') {
    endpoint <- "https://api.subquery.network/sq/AcalaNetwork/acala-incentives"
  } else if (tolower(network) == 'karura') {
    endpoint <- "https://api.subquery.network/sq/AcalaNetwork/karura-incentives"
  } else {
    stop("Network not found; must be one of 'acala' or 'karura'")
  }
  if (staging) endpoint <- endpoint %+% stagingStr

  method <- "claimRewards"
  edges <- "id addressId tokenId pool actualAmount deductionAmount blockId extrinsicId timestamp"
  filter <- ' filter: {blockId: { lessThan: "1639493", greaterThan: "1638215" }}'
  res <- get_graph(endpoint, method, edges, window, filter, endpage)
  res[, tokenId := fixToken(tokenId)]
  res[, pool := fixToken(pool)]

  res <- merge(res, tokens, by.x = "tokenId", by.y="Token")
  # res[, actualAmount := as.numeric(actualAmount) / 10**as.numeric(decimals)]
  # res[, deductionAmount := as.numeric(deductionAmount) / 10**as.numeric(decimals)]
  res

}

r_in <- getRewards_acala_incentives("Acala", window = 4)
r_in[, pool := fixToken(pool)]
r_in <- r_in[pool == "dex-lp://AUSD/iBTC" & tokenId == "AUSD"]
setnames(r_in, names(r_in), names(r_in) %+% "_in")
r_in <- r_in[, .(id_in, addressId_in, actualAmount_in, blockId_in)]
tail(r_in, 2)

comb <- merge(trace, r_in, by.x = "id_sq", by.y = "id_in", all = TRUE)
comb[, diff := abs(as.numeric(actualAmount_sq) - as.numeric(actualAmount_in))]
comb[diff > 0]


r_ss <- get_subscan_events(nobs = 1000, network = 'Acala', start_page = 1, module = 'incentives', call = 'ClaimRewards', block = NULL)$incentives_ClaimRewards
stopifnot(min(r_ss$block_num) <= 1638215)

r_ss[, token0Id := fixToken(token0Id)]
r_ss[, token1Id := fixToken(token1Id)]
r_ss[, rewardToken := fixToken(rewardToken)]
r_ss <- r_ss[block_num >= 1638215 & block_num <= 1639493 & rewardToken == "AUSD"]
r_ss <- merge(r_ss, tokens, by.x = "rewardToken", by.y="Token")
r_ss[, actualAmount := as.numeric(actualAmount) / 10**as.numeric(decimals)]
r_ss <- r_ss[, .(event_index, AccountId, actualAmount)]
setnames(r_ss, names(r_ss), names(r_ss) %+% "_ss")
tail(r_ss, 2)

comb2 <- merge(trace, r_ss, by.x = "id_sq", by.y = "event_index_ss", all = TRUE)
comb2[, diff := abs(as.numeric(actualAmount_sq) - as.numeric(actualAmount_ss))]
comb2[diff > 0]



getHourlyPools_acala_dex <- function(network, window = 1, filter = '', staging = FALSE) {

  if (tolower(network) == 'acala') {
    endpoint <- "https://api.subquery.network/sq/AcalaNetwork/acala-dex"
  } else if (tolower(network) == 'karura') {
    endpoint <- "https://api.subquery.network/sq/AcalaNetwork/karura-dex"
  } else {
    stop("Network not found; must be one of 'acala' or 'karura'")
  }
  if (staging) endpoint <- endpoint %+% stagingStr

  method <- "hourlyPools"
  filter <- ' filter: {updateAtBlockId: {in: ["1638007", "1639638"]}}'
  edges <- "id
            token0 {decimals, name}
            token1 {decimals, name}
            token0Amount
            token1Amount
            totalTVL
            token0TVL
            token1TVL
            updateAtBlock {id}"
  res <- get_graph(endpoint, method, edges, window=1, filter = filter)

  # Replace foreign assets
  res[, token0.name := fixToken(token0.name)]
  res[, token1.name := fixToken(token1.name)]
  res[, id := fixToken(id)]

  res[, totalTVL := as.numeric(totalTVL) / 1e18]
  res

}



tmp <- getPoolStats_acala_dex("Acala", window = 6)
unique(tmp$id)

hourly <- getHourlyPools_acala_dex("Acala", window = 1)
strsplit(hourly$id, "-")
  
daily <- getDailyPool_acala_dex("Acala", window = 1, filter = '')
unique(daily$poolId)


# library(googlesheets4)
# library(googledrive)
# drive_auth(email="roger@laminar.one")
# gs4_auth()
# tmp <- read_sheet("https://docs.google.com/spreadsheets/d/1d49RhOV5C_u5KZpjwVJKEug53R6iGF-h6Pjs9bCTqPY/edit#gid=126763249")


  library(readxl)
  rd <- read_xlsx("~/Downloads/Recovery(INTERNAL).xlsx", sheet = 6)[, 1:8] %>% 
    as.data.table
  rd[, .N]
  # e <- strsplit(rd$eventId, "-")
  # rd[, block := NULL]
  # for (ii in 1:nrow(rd)) rd$block[ii] <- as.numeric(e[ii][[1]][1])
  
  rd[1:2]
  
  dex <- get_subscan_events(nobs = 50000, network = 'Acala', start_page = 1, module = 'dex')

  remliq <- dex$dex_RemoveLiquidity
  remliq[, eventId := block_num %+% "-" %+% event_idx]
  remliq[, token0Id := fixToken(token0Id)]
  remliq[, token1Id := fixToken(token1Id)]
  remliq[, .N]
  for (ii in 1:nrow(remliq)) remliq$address[ii] <- py$pk_convert(remliq$AccountId[ii][[1]], 10)
  remliq <- merge(remliq, tokens, by.x = "token0Id", by.y="Token", all.x = TRUE) %>%
    setnames("decimals", "decimals0")
  remliq[is.na(decimals0), .N]
  remliq[, Name := NULL]
  remliq[, token0Amount := -as.numeric(token0Amount) / 10 ** as.numeric(decimals0)]
  remliq <- merge(remliq, tokens, by.x = "token1Id", by.y="Token", all.x = TRUE) %>%
    setnames("decimals", "decimals1")
  remliq[is.na(decimals1), .N]
  remliq[, Name := NULL]
  remliq[, token1Amount := -as.numeric(token1Amount) / 10 ** as.numeric(decimals1)]
  head(remliq,2)

  remliq[is.na(decimals1)]
  
  addliq <- dex$dex_AddLiquidity
  addliq[, eventId := block_num %+% "-" %+% event_idx]
  addliq[, token0Id := fixToken(token0Id)]
  addliq[, token1Id := fixToken(token1Id)]
  addliq[, .N]
  for (ii in 1:nrow(addliq)) addliq$address[ii] <- py$pk_convert(addliq$AccountId[ii][[1]], 10)
  addliq <- merge(addliq, tokens, by.x = "token0Id", by.y="Token", all.x = TRUE) %>%
    setnames("decimals", "decimals0")
  addliq[, Name := NULL]
  addliq[, token0Amount := as.numeric(token0Amount) / 10 ** as.numeric(decimals0)]
  addliq <- merge(addliq, tokens, by.x = "token1Id", by.y="Token", all.x = TRUE) %>%
    setnames("decimals", "decimals1")
  addliq[, Name := NULL]
  addliq[, token1Amount := as.numeric(token1Amount) / 10 ** as.numeric(decimals1)]
  addliq[, .N]

  rd_rem <- merge(rd, remliq, by.x = c("who","block"), by.y = c("address", "block_num"))
  rd_add <- merge(rd, addliq, by.x = c("who","block"), by.y = c("address", "block_num"))

  rd_new <- rbind(rd_rem[, .(who, eventId.x, currencyId0, token0Id, pool0, token0Amount, currencyId1, token1Id, pool1, token1Amount)],
  rd_add[, .(who, eventId.x, currencyId0, token0Id, pool0, token0Amount, currencyId1, token1Id, pool1, token1Amount)])
  rd[, .N]  
  rd_new[, .N]  
  rd_rem[, .N]
  rd_add[, .N]

  names(rd)
  names(rd_new)
  rd_test <- merge(rd, rd_new[, .(who, eventId.x)], by.x="eventId", by.y = "eventId.x", all = TRUE)
  rd_test[is.na(who.y)]
  unique(rd_test$who.x)
  
  tmp <- rd[, .N, by = who] %>% setorder(N)
  tmp_new <- rd_new[, .N, by = who] %>% setorder(N)
  
  rd[who == '23eCXs2tg7xv2btSHtb3m79eiN96KZtQ6GMpWpg6EKDQnKB2']
  rd_new[who == '23eCXs2tg7xv2btSHtb3m79eiN96KZtQ6GMpWpg6EKDQnKB2']
  
  
  
  # nobs = 100; network = 'Astar'; module = ''; call = ''; page = 1
  # nobs = 500; network = 'Karura'; module = 'dex'; call = 'Swap'; page = 1; start_page = 1
  # nobs = 100; network = 'Acala'; module = 'incentives'; call = ''; start_page = 1; extract = TRUE
  # nobs = 100; network = 'Karura'; module = 'loans'; call = 'PositionUpdated'; start_page = 1; extract = TRUE



  
```

# Acala {.tabset}

Row
----

### Collateral Deposited

This report pulls the most 60 days of `loans.UpdatePosition` events from Subscan and compares those to the `PositionUpdate` entity values shown by the `acala-loans-subql` project.  There are many instances where the collateral value is zero.  We focus on the most interesting observations by requiring that the collateral value is non-zero in both data sources.  There are `r nrow(a_deposit_match)` instances where the values match and `r nrow(a_deposit_not)` where they do not match.  Here is a sampling of the non-matching observations.

```{r a_deposit}

knitr::kable(head(a_deposit_not, 15)) %>%
  kable_styling()

```

Row
----

### Debit

This report pulls the most 60 days of `loans.UpdatePosition` events from Subscan and compares those to the `PositionUpdate` entity values shown by the `acala-loans-subql` project.  There are `r nrow(a_debit_match)` instances where the values match and `r nrow(a_debit_not)` where they do not match.  Here is a sampling of the non-matching observations.

```{r a_debit}

knitr::kable(head(a_debit_not, 15)) %>%
  kable_styling()

```

Sources: 

* Subscan - https://acala.subscan.io/

* Subquery - https://explorer.subquery.network/subquery/AcalaNetwork/acala-loan


# Karura {.tabset}

Row
----

### Collateral Deposited

This report pulls the most 60 days of `loans.UpdatePosition` events from Subscan and compares those to the `PositionUpdate` entity values shown by the `acala-loans-subql` project.  There are many instances where the collateral value is zero.  We focus on the most interesting observations by requiring that the collateral value is non-zero in both data sources.  There are `r nrow(k_deposit_match)` instances where the values match and `r nrow(k_deposit_not)` where they do not match.  Here is a sampling of the non-matching observations.

```{r k_deposit}

knitr::kable(head(k_deposit_not, 15)) %>%
  kable_styling()

```

Row
----

### Debit

This report pulls the most 60 days of `loans.UpdatePosition` events from Subscan and compares those to the `PositionUpdate` entity values shown by the `acala-loans-subql` project.  There are `r nrow(k_debit_match)` instances where the values match and `r nrow(k_debit_not)` where they do not match.  Here is a sampling of the non-matching observations.

```{r k_debit}

knitr::kable(head(k_debit_not, 10)) %>%
  kable_styling()

```

Sources: 

* Subscan - https://karura.subscan.io/

* Subquery - https://explorer.subquery.network/subquery/AcalaNetwork/karura-loan

